AP/PA Tables ITHIM Global

### 2024-03-13 summary_tables_PA_AP.Rmd
Use co2_emission instead of conc

---
title: "AP/PA Tables ITHIM Global"
date: "`r format(Sys.time(), '%d %B, %Y')`"
params:
  output_version: ''
output:
  html_document: 
    toc: true
    toc_depth: 5
    toc_float: true
  word_document: default
  pdf_document: default
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(comment=NA, prompt=FALSE, cache=FALSE, echo=F, results='asis')

@@

#   - CO2_conc: table detailing the CO2 concentration levels for each scenario for all cities

@@

# create summary table of CO2 concentrations in each scenario
co2_conc <- list()
td <- NA

@@

  # extract CO2 concentrations
  td <- round(colSums(io[[city]]$outcomes$co2_conc, na.rm = T), 1) %>% 
    as.data.frame() %>% tibble::rownames_to_column()
  names(td) <- c('Scenario', city)

  # create one dataframe containing all cities
  if (length(co2_conc) == 0)
    co2_conc <- td
  else
    co2_conc <- left_join(co2_conc, td)

@@

# Dan: here the order is different (bus before car)
# co2_conc$Scenario <- new_scen_names
co2_conc$Scenario <- sapply(co2_conc$Scenario, FUN = get_qualified_scen_name)

# print to html
print(kable(co2_conc))

@@

  # CO2
  # extract CO2 transport emissions for each scenario
  td <- round(colSums(io[[cities[x]]]$outcomes$co2_conc, na.rm = T), 1) %>%
    as.data.frame() %>% tibble::rownames_to_column()
  names(td) <- c('Scenario', 'CO2')

@@

# create output Excel file containing the basic PM2.5 and CO2 exposure / concentration information
output_file <- paste0('results/multi_city/AP/desc_stats_', output_version ,".xlsx")
writexl::write_xlsx(list(PM_2.5_emission_inventory = sl,
                         CO2_conc = co2_conc,
                         summary_stats_PM2.5_CO2 = bind_rows(l)), path = output_file)

>>>>

---
title: "AP/PA Tables ITHIM Global"
date: "`r format(Sys.time(), '%d %B, %Y')`"
params:
  output_version: ''
output:
  html_document: 
    toc: true
    toc_depth: 5
    toc_float: true
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(comment=NA, prompt=FALSE, cache=FALSE, echo=F, results='asis')

@@

#   - C02_emission_inventory: table detailing the CO2 emission levels for each scenario for all cities

@@

# create summary table of CO2 concentrations in each scenario
co2_emission_inventory <- list()
td <- NA

@@

  # extract CO2 concentrations
  td <- round(colSums(io[[city]]$outcomes$co2_emission_inventory, na.rm = T), 1) %>% 
    as.data.frame() %>% tibble::rownames_to_column()
  names(td) <- c('Scenario', city)

  # create one dataframe containing all cities
  if (length(co2_emission_inventory) == 0)
    co2_emission_inventory <- td
  else
    co2_emission_inventory <- left_join(co2_emission_inventory, td)

@@

# Dan: here the order is different (bus before car)
# co2_emission_inventory$Scenario <- new_scen_names
co2_emission_inventory$Scenario <- sapply(co2_emission_inventory$Scenario, FUN = get_qualified_scen_name)

# print to html
print(kable(co2_emission_inventory))

@@

  # CO2
  # extract CO2 transport emissions for each scenario
  td <- round(colSums(io[[cities[x]]]$outcomes$co2_emission_inventory, na.rm = T), 1) %>%
    as.data.frame() %>% tibble::rownames_to_column()
  names(td) <- c('Scenario', 'CO2')

@@

# create output Excel file containing the basic PM2.5 and CO2 exposure / concentration information
output_file <- paste0('results/multi_city/AP/desc_stats_', output_version ,".xlsx")
writexl::write_xlsx(list(PM_2.5_emission_inventory = sl,
                         co2_emission_inventory = co2_emission_inventory,
                         summary_stats_PM2.5_CO2 = bind_rows(l)), path = output_file)
